Algorithmic Approaches to Match Degraded Land Impressions

### 2017-10-22 degraded-paper.Rmd
fig 13 now not blind

mypaste <- function(strings) { paste("Method", strings) }

ggplot(data = final_result, aes(x = match, y = score, fill = match)) +
    geom_boxplot() +
    coord_flip() +
    facet_wrap(~method, nrow = 4, labeller = labeller(method = mypaste)) +
    scale_fill_brewer("Bullet Land Pairs", palette="Paired") +
    theme_bw() +
    theme(legend.background = element_rect(colour="grey75"),
          axis.text.y = element_blank(),
          axis.title.y = element_blank())
```

>>>>

dframe <- data.frame(expand.grid(match=c("Known non-matches (KNM)", "Known matches (KM)"), method=1:4))
dframe$x <- c(0.75, 2.25)[as.numeric(as.factor(dframe$match))]
dframe$y <- c(0.15, 0.9)[as.numeric(as.factor(dframe$match))]
idx <- with(dframe, which(method==1 & match=="Known non-matches (KNM)"))
dframe$y[idx] <- 0.2
idx <- with(dframe, which(method==1 & match=="Known matches (KM)"))
dframe$y[idx] <- 0.875
idx <- with(dframe, which(method==3 & match=="Known matches (KM)"))
dframe$y[idx] <- 0.7
idx <- with(dframe, which(method==4 & match=="Known matches (KM)"))
dframe$x[idx] <- 1.45

mypaste <- function(strings) { paste("Method", strings) }
ggplot(data = final_result, aes(x = match, y = score, fill = match)) +
    geom_boxplot() +
    coord_flip() +
    facet_wrap(~method, nrow = 4, labeller = labeller(method = mypaste)) +
    scale_fill_brewer("Bullet Land Pairs", palette="Paired") +
    theme_bw() +
    theme(legend.background = element_rect(colour="grey75"),
          axis.text.y = element_blank(),
          axis.title.y = element_blank()) +
  theme(legend.position="none") +
  geom_text(aes(x=x,y=y, label=match), colour="grey40", data=dframe)
